\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}


\begin{document}

\section{Cristian Garcia}\label{cristian-garcia}

Data Scientist + Developer with Background in Maths \& Physics

\subsubsection{Contact Info}\label{contact-info}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  email: cgarcia.e88@gmail.com
\item
  cel: (+57) 3148627978
\item
  linkedin: \url{https://www.linkedin.com/in/cgarciae/}
\end{itemize}

\subsubsection{Summary}\label{summary}

Data Scientist and Developer with background in maths and physics. My
two passions are programming and deep learning, I consider myself a
strong programmer/developer given my experience creating real world
applications and my love for functional programming, however my area of
interest has always been scientific computation and enjoy programming
deep neural networks in tensorflow.

\subsubsection{Experience}\label{experience}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Toptal Developer} - Coming soon!
\item
  \textbf{Kiwi Campus} - Lead Data Scientist (current): Designed the
  curriculum of various Data Science/ML courses. Evaluated various IoT
  platforms. Investigated technologies such a TensorFlow and OpenCV to
  run ML algorithms in IoT devices.
\item
  \textbf{BD Guidance} - Data Scientist: Designed the curriculum of
  various Data Science/ML courses. Evaluated various IoT platforms.
  Investigated technologies such a TensorFlow and OpenCV to run ML
  algorithms in IoT devices.
\item
  \textbf{Senseta} - Data Scientist (2016): Developed a Linux and
  Windows python application for HR software to measure employee
  productivity. Cleaned and analyzed large datasets using Spark and
  Zeppelin. Created a service in Python for Entity extracting using
  NLTK. Created a generic ML prediction service using Scikit Learning
  and Flask.
\item
  \textbf{PTK} - Mathematical Developer (2015): Researched on strategies
  to optimize pickup planning in warehouses. Researched on technologies
  to create scalable multi-tenant software.
\item
  \textbf{AristaDev} - Cofounder/Developer: Cofounder and main developer
  on an Augmented Reality platform. I developed the mobile client and
  backend of Arista using tecnologies such as Unity3D, Elixir, Docker,
  Nginx, and PostgreSQL.
\end{itemize}

\subsubsection{Open Source}\label{open-source}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://github.com/cgarciae/phi}{phi}: fluent functional
  programming in python.
\item
  \href{https://github.com/cgarciae/dataget}{dataget}: download, extract
  and process popular machine learning datasets with a single line of
  bash or python.
\item
  \href{https://github.com/cgarciae/tfinterface}{tfinterface}: develop
  structured models in tensorflow and get lots functionality for free
\item
  \href{https://github.com/cgarciae/cybrain}{cybrain}: fast neural
  network in python, written in cython.
\item
  \href{https://github.com/cgarciae/karma}{karma}: MVC library for
  Unity3D
\end{itemize}

\subsubsection{Areas of Interest}\label{areas-of-interest}

Deep Learning/Neural Networks, Artificial Intelligence,
Optimization/Heuristics, Mathematical Modelling, Agent-based Simulation,
Network Analysis, Functional Programming, Distributed Systems

\subsubsection{Languages}\label{languages}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Spanish: native
\item
  English: C2, bilingual school since 4 years old
\end{itemize}

\subsubsection{Programming Languages}\label{programming-languages}

Python: 6+ years, Matlab: 6+ years, Mathematica : 3+ years, C\#: 2+
years, Elixir: 2+ years, JavaScript: 1+ years, Dart: 1+ years, Cython:
1+ years, C, Haskell, Java, Lisp, Scala, Elm, Rust, Coq, Julia

\subsubsection{Tools/Frameworks}\label{toolsframeworks}

\textbf{Data Science:} \href{https://www.tensorflow.org/}{Tensorflow}
(python), \href{http://scikit-learn.org}{Scikit Learn} (python),
\href{http://pandas.pydata.org/}{Pandas},
\href{http://www.numpy.org/}{Numpy},
\href{https://networkx.github.io/}{NetworkX} (python),
\href{http://spark.apache.org/}{Spark} (scala/python),
\href{http://www.anylogic.com/}{AnyLogic} (java)

\textbf{Development:} \href{http://www.phoenixframework.org/}{Phoenix
Framework} (elixir), \href{http://flask.pocoo.org/}{Flask} (python),
\href{http://graphene-python.org/}{Graphine} (graphql + python),
\href{https://git-scm.com/}{Git}, \href{https://unity3d.com/}{Unity3D}
(c\#), \href{https://www.postgresql.org/}{PostgreSQL},
\href{https://www.mongodb.com/}{MongoDB},
\href{https://github.com/rethinkdb/rethinkdb}{RethinkDB}

\subsubsection{Community}\label{community}

\subparagraph{Organizations/Groups}\label{organizationsgroups}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Co-founder of
  \href{https://www.facebook.com/groups/1766056600304468}{Machine
  Learning Colombia}
\item
  Co-founder of \href{https://www.meetup.com/es-ES/ml-medellin}{Machine
  Learning Meetup Medellin}
\item
  Founder of
  \href{https://github.com/colomb-ia/mision-vision}{colomb-ia}
\end{itemize}

\subparagraph{Talks/Conferences}\label{talksconferences}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://www.meetup.com/es-ES/ml-medellin/events/231887878/}{Deep
  Learning with TensorFlow} at
  \href{https://www.meetup.com/es-ES/ml-medellin}{Machine Learning
  Meetup Medellin}
\item
  \href{https://www.meetup.com/es-ES/ml-medellin/events/232587669/}{Introduction
  to Spark} at \href{https://www.meetup.com/es-ES/ml-medellin}{Machine
  Learning Meetup Medellin}
\item
  \href{https://www.meetup.com/es-ES/Big-Data-Science-Bogota/events/233975872}{Deep
  Learning \& TensorFlow} at
  \href{https://www.meetup.com/es-ES/Big-Data-Science-Bogota/}{Big Data
  \& Data Science Bogotá}
\item
  Deep Learning with TensorFlow at \href{http://pataconf.com/}{pataconf}
\item
  Introduction to Deep Learning with TensorFlow at
  \href{http://www.pycon.co/}{PyCon Colombia}
\item
  Scalable Deep Learning with TensorFlow at
  \href{http://scaleconfco.com/}{ScaleConf Colombia}
\item
  \href{https://www.meetup.com/es-ES/ml-medellin/events/238072044/}{TensorFlow
  for Developers} at
  \href{https://www.meetup.com/es-ES/ml-medellin}{Machine Learning
  Meetup Medellin}
\end{itemize}

\subsubsection{Personal Projects}\label{personal-projects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://github.com/cgarciae/supervised-avanzado-german-traffic-signs/tree/feature/solucion-basica}{Basic
  ConvNet for the German Traffic Signs Dataset}
\item
  \href{https://github.com/cgarciae/supervised-avanzado-german-traffic-signs/tree/feature/batch-norm-squeeze-net}{SqueezeNet
  with Batch Normalization on TensorFlow}
\item
  \href{https://github.com/cgarciae/supervised-avanzado-german-traffic-signs/tree/feature/dense-net-elu-2}{An
  implementation DenseNet with ELU layers on TensorFlow}
\end{itemize}

\end{document}
