\cvsection{Experience}
\begin{cventries}

  \cventry
    {Senior Machine Learning Engineer}
    {Snappr Inc}
    {Medellin}
    {Current}
    {
    Developed Machine Learning applications to automate tasks throughout the company such as client sales prediction, demand forecast, photo aesthetics prediction, image clustering, models using GIS data, and more using both Machine Learning and Deep Learning.
    }

  \cventry
    {Machine Learning Engineer}
    {Landing AI}
    {Medellin}
    {1 year}
    {
    Developed Automatic Visual Inspection solutions using Deep Learning techniques for clients in the automotive industry. Developed an internal tool to that enabled training deep learning models with small datasets. Worked on a generative model for images using GANs.
    }

  \cventry
    {Lead Engineer in Computer Vision}
    {Bigbang Media}
    {Los Angeles, CA}
    {6 months}
    {
    Developed various Deep Learning models for tasks like video classification and event detection in videos using distributed Tensorflow, TPUs, and Dataflow.
    }
  
  \cventry
    {Lead Data Scientist}
    {Kiwi Campus}
    {Berkeley}
    {1 year}
    {
    Lead Data Scientist and Deep Learning developer for autonomous driving delivery robots. Used
    Deep Learning techniques like CNNs and RNNs for autonomous control,
    with technologies such as TensorFlow, ROS, Jupyter, Flask.
    }


  \cventry
    {Toptal Developer}
    {Toptal}
    {International}
    {Since 2017}
    {
      Toptal connects the top 3 \% of freelance talent all over the world. \href{https://www.toptal.com/resume/cristian-garcia}{\textbf{Profile}}
    }

  \cventry
    {Data Scientist}
    {BD Guidance}
    {Colombia}
    {1 year}
    {
    Data Scientist: Designed the curriculum of various
    Data Science/ML courses. Evaluated various IoT platforms. Investigated
    technologies such a TensorFlow and OpenCV to run ML algorithms in IoT
    devices.
    }

  \cventry
    {Data Scientist}
    {Senseta}
    {Medellin, Colombia}
    {1 year}
    {
    Developed a Linux and Windows python
    application for HR software to measure employee productivity. Cleaned
    and analyzed large datasets using Spark and Zeppelin. Created a service in
    Python for Entity extracting using NLTK. Created a generic ML prediction
    service using Scikit Learning and Flask
    }
  \cventry
    {Mathematical Developer}
    {PTK}
    {Colombia}
    {8 months}
    {
    Researched on strategies to optimize
    pickup planning in warehouses. Researched on technologies to create
    scalable multi-tenant software
    }
  \cventry
    {Cofounder - Developer}
    {AristaDev}
    {Colombia}
    {2 years}
    {
    Cofounder and main developer on an
    Augmented Reality platform. I developed the mobile client and backend
    of Arista using tecnologies such as Unity3D, Elixir, Docker, Nginx, and
    PostgreSQL.
    }
\end{cventries}
